---
title: "Assessment 1"
author: "Vibhore Dhanda s4653077"
date: "3/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RMarkdown editing


**R Markdown** Markdown is a lightweight markup language and created by John Gruber in 2004. Nowadays markdown is one of the world’s most popular markup languages. The file extension of a Markdown file is .md or .markdown. To compile a markdown file user needs an application capable of processing markdown files like Microsoft Word, Dillinger, etc. These applications utilize a Markdown parser which converts a markdown file to printable HTML code. 

<https://rmarkdown.rstudio.com/lesson-8.html>.

# 6

```{r}
library(tidyverse)
fastfood <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```
# 7
 
```{r}

head(fastfood, 10) 

knitr::kable(head(fastfood[, 1:5],10))

```

#Part 2

# 8
 
```{r}

knitr::kable((subset(fastfood, calories>1000)))

```

# 9
 
```{r}
dont_eat_this<-knitr::kable((subset(fastfood, total_fat>40 & total_carb>80)))
print(dont_eat_this)
```

#10
```{r}
heavy_food<-knitr::kable((subset(fastfood, calories>500)) %>%  count(restaurant)) 
print('Heavy')
print(heavy_food)
heavy_food<-knitr::kable((subset(fastfood, calories>250 & calories < 500))%>%  count(restaurant)) 
print('Average')
print(heavy_food)
heavy_food<-knitr::kable((subset(fastfood, calories<250))%>%  count(restaurant)) 
print('Low')
print(heavy_food)
```

#11

```{r}
library(skimr)
skim(fastfood) %>%  summary() 
```

#12
```{r}
knitr::kable(fastfood %>% group_by(restaurant) %>%  count(restaurant) %>% arrange(desc(n)))
```

#13
```{r}
knitr::kable(fastfood %>% group_by(restaurant) %>% summarise(calories = mean(calories)))
```

#14
```{r}
average_calories<-knitr::kable(fastfood %>% group_by(restaurant) %>% summarise(calories = mean(calories)))
print(average_calories)
max_fat<-knitr::kable(fastfood %>% group_by(restaurant) %>% summarise(total_fat =max(total_fat)))
print(max_fat)
min_cholesterol<-knitr::kable(fastfood %>% group_by(restaurant) %>% summarise(cholesterol= min(cholesterol)))
print(min_cholesterol)
```
#15
```{r}
fastfood %>% group_by(restaurant) %>% summarise(total_fat = sum(total_fat)) %>%    
ggplot() +   aes(x = restaurant, fill = restaurant, weight = total_fat) +   geom_bar() +   scale_fill_hue() +   labs(x = "Restaurant_Type", y = "Total fats", title = "Chart", subtitle = " Fat with respect to Restaurant", caption = "Total Fat with respect to each Restaurant", fill = "Legend")  
```
<p>There are two restaurants: one is Burger king and second is Taco Bell are having highest quantity of fats. There is higher total amount of fat compared to other restaurants. The lowest quantity of fat is with the Chick Fil A. </p>

#16
```{r}
cholesterol_sodium<- fastfood$cholesterol+fastfood$sodium
fastfood[19]<-cholesterol_sodium
fastfood <- fastfood[ -c(18) ]
```

#17
```{r}
observations<-head((subset(fastfood, restaurant=='Mcdonalds')),60)
p<-ggplot(data.frame(observations),aes(sugar, protein)) 
p+ geom_point()
```
#18
```{r}
factors1 <- factor(fastfood$restaurant)
levels(factors1)
```
#19
```{r}
labels=c("low", "medium", "high")
calories_type<-cut_number(fastfood$calories,3,labels)
```
#20
```{r}
fastfood %>% group_by(restaurant) %>%    
ggplot() +   aes(x = fastfood$restaurant, fill = fastfood$restaurant, weight = calories) +   geom_bar() +   scale_fill_hue() +   labs(x = "Restaurants Type", y = "Calories Type", title = "Calories/ Restaurant", subtitle = "Calories per Restaurant", caption = "Graph for Calories per Restaurant", fill = "Legend")  
```
#21

```{r}
trans_fat_percent<-knitr::kable(fastfood %>% summarise(trans_fat_percent =trans_fat/total_fat*100 ))
```
#22

```{r}
fastfood %>% group_by(restaurant) %>%    
ggplot() +   aes(x = fastfood$restaurant, fill = fastfood$restaurant, weight = trans_fat) +   geom_bar() +   scale_fill_hue() +   labs(x = "Restaurant", y = "trans_fat", title = "Trans fat per restaurant", subtitle = "trans_fat/Restaurant", caption = "trans_fat/Restaurant", fill = "Legend") 
```
#23
```{r}
knitr::kable(fastfood %>% group_by(restaurant) %>% summarise(total_fat = mean(total_fat)))
```
#24
```{r}
fastfood %>% group_by(restaurant) %>%    
ggplot() +   aes(x = fastfood$restaurant, fill = fastfood$restaurant, weight = total_fat) +   geom_bar() +   scale_fill_hue() +   labs(x = "Restaurant", y = "total_fat", title = "total fat per restaurant", subtitle = "total_fat/Restaurant", caption = "total_fat/Restaurant", fill = "Legend") 
```
#end of file






